---
title: "Well Being Index"
author: "Ayush Patel"
date: "`r Sys.Date()`"
output: 
  html_document: 
    css: STATAcode.css
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css ,echo = FALSE}
h1, h2, h3 {
  text-align: center;
  color: #303960;
}
```

__Nepal Well Being Index __

MICS 2014 data is used to create this Index. Through out this document a convention is maintained where the STATA code will be provided as reference to the equivalent  R code.

The STATA code provided as referecne will show up as follows[^1]:

:::statacode
Reference STATA code will appear in such boxes.
:::

[^1]: Icons made by <a href="https://www.flaticon.com/authors/xnimrodx" title="xnimrodx">xnimrodx</a> from <a href="https://www.flaticon.com/" title="Flaticon"> www.flaticon.com</a>

# Libraries

```{r libraries}
library(here)
library(tidyverse)
library(haven)
library(janitor)
library(magrittr)
library(knitr)
library(kableExtra)
library(gt)
library(anthro)
```

# Step1: Data Preparation

Comment from STATA code:

_Selecting main variables from WM and CH recode and merging with HL recode._  

## Step 1.1: CH - Children's Level (Children Under 5)


:::statacode
use "$workingfolder_in\ch.dta", clear //Change to the corresponding CH-file// 
:::

Note that the STATA code imports the .dta file, we have the same data in .sav format. We will be using these files.

```{r dataimport_ch}
ch_dta <- read_sav(here("data","ch.sav"))

```

### Step1.1a: Key variable for merging


:::statacode
rename _all, lower 
:::

```{r}
ch_dta <- clean_names(ch_dta)
```

:::statacode
gen double ind_id = hh1*100000 + hh2*100 + ln 

//Please check length of variables for a correct generation of the id variable// 

format ind_id %20.0g 

label var ind_id "Individual ID" 
:::

```{r Indid_ch}
ch_dta %<>%
  mutate(
    ind_id = structure(
      hh1*100000 + hh2*100 + ln,
      label = "Individual ID"
    )
  )
```


:::statacode
duplicates report ind_id 

duplicates tag ind_id, gen(duplicates) 

tab ln if duplicates!=0 //A number of children are not listed in the household// 
:::

```{r ch_duplicate_ind_id}
(nrow(ch_dta) == length(unique(ch_dta$ind_id)) 
 & sum(is.na(ch_dta$ind_id)) == 0) ## Returns on True if ind_id has no duplicates

# creating a table of ind_ids that are duplicatess
table(ch_dta$ind_id) %>% 
  as.data.frame %>% 
  filter(Freq>1) -> ch_dta_duplicate_ind_id

ch_dta %<>%
  mutate(
    duplicates = ind_id  %in% ch_dta_duplicate_ind_id$Var1
  ) 

ch_dta %>%
  filter(duplicates == 1) %>% 
  tabyl(ln, show_na = T)
```

:::statacode
bys ind_id: gen line = (_n) 

replace ind_id =  hh1*100000 + hh2*190 + line if duplicate!=0 //We assume consecutive hh line starting at 90// 
 
duplicates report ind_id //We should not have any duplicate at this stage// 
 
gen child_CH = 1 //Identification variable for observations in CH recode// 
:::

```{r removing_duplicates_if_any}
ch_dta %<>%
  group_by(ind_id) %>% 
  mutate(line = n()) %>% 
  ungroup()
  
ch_dta %<>% 
  mutate(
    ind_id = structure(
      ifelse(duplicates != 0,
             hh1*100000 + hh2*190 + line, ind_id),
      label = "Individual ID"
    ),
    child_CH = 1
  )

(nrow(ch_dta) == length(unique(ch_dta$ind_id)) 
 & sum(is.na(ch_dta$ind_id)) == 0) ## Returns on True if ind_id has no duplicates
```

### Step 1.1b: Children Nutrition


__Variable Sex__

:::statacode
tab hl4, miss //Check the variable for "sex" has "1" for male, "2" for female and all missing values are "."// 

gen gender = hl4 

desc gender 

tab gender 

label define gender 1"male" 2"female", replace 

label values gender gender 
:::


```{r variable_sex_nutrition}
str(ch_dta$hl4)

ch_dta %<>%
  mutate(
    gender = structure(
      hl4,
      labels = c("male"  = 1, "female" = 2) 
    )
  )

str(ch_dta$gender)
```

__Variable Age__

:::statacode
ta cage,m //Check all missing values are "."// 

ta caged,m //Check all missing values are "."// 

codebook cage caged //Check unit of measure – in this case age is measured in months// 

clonevar age_months = cage  

clonevar age_days = caged 

replace age_months = . if cage==99 //No missing data here// 

gen str6 ageunit = "days" //We define the unit of measure, in this case age is measured in months, otherwise please change to ageunit = "days"// 
lab var ageunit "Days" 
:::


```{r variable_age_nutrition}
sum(is.na(ch_dta$cage))

sum(is.na(ch_dta$caged))

ch_dta %<>%
  mutate(
    age_months = ifelse(cage==99, NA, cage),
    age_days = caged,
    ageunit = structure("days", label = "Days")
  )
```

__Variable body weight[^2]__

[^2]: It must be in kilograms

:::statacode
ta an3, miss //Check all missing values are "."//  

codebook an3 //Check unit of measure – in this case weight is measured in kilograms// 

clonevar weight = an3  

desc weight  

replace weight = .  if an3>=99 //All missing values or out of range are replaced as "."// 

tab an2 an3 if an3>=99 | an3==., miss //an2: result of the measurement// summ weight 
:::

```{r variable_bodyweight_nutrition}
sum(is.na(ch_dta$an3))

str(ch_dta$an3)

ch_dta %<>%
  mutate(
    weight = ifelse(an3 >=99, NA, an3)
  )

ch_dta %>% 
  filter(an3 >=99 | is.na(an3)) %>% 
  tabyl(an2, an3,show_na = T) %>%
  knitr::kable()%>%
  kableExtra::kable_styling()
  
  
  
  
  
```


__Variable height[^3]__

[^3]: It mus be in centimeters

:::statacode
ta an4, miss //Check all missing values are "."//  

codebook an4 //Check unit of measure – in this case age is measured in centimetres// 

clonevar height = an4 

desc height  

replace height = . if an4>=999 //All missing values or out of range are replaced as "."// 

summ height ## Not sure what this command means

codebook an4a gen measure = "l" if an4a==1 //Child measured lying down// 
replace measure = "h" if an4a==2 //Child measured standing up// 

replace measure = " " if an4a==. // No information  

replace measure = " " if an4a==9 //Replace with " " if unknown or missing//

:::


```{r varible_height_nutrition}
sum(is.na(ch_dta$an4))

str(ch_dta$an4)

ch_dta %<>%
  mutate(
    height = ifelse(an4 >= 999, NA, an4),
    measure = case_when(
      is.na(an4a) ~ NA_character_,#Notice the deviation from the stata script
      an4a == 9 ~ NA_character_,#Notice the deviation from the stata script
      an4a == 1 ~ "l",
      an4a == 2 ~ "h"
    )
  )
```

__The above mentioned deviation of using `NA` instead of " " is delibrate and retrospective. The `anthro_zscores()` does not take any other values that `"l" | "L" | "H" | "h" | NA` for the `measure` argument.__

:::statacode
tab an2 an4 if an4>=999 | an4==., miss  

tab measure,m 

:::

```{r tabs_height_variables}

ch_dta %>% 
  filter(an4 >= 999 | is.na(an4)) %>% 
  tabyl(an2, an4, show_na = T)%>%
  knitr::kable()%>%
  kableExtra::kable_styling()
  
ch_dta %>% 
  tabyl(measure, show_na = T) %>%
  knitr::kable()%>%
  kableExtra::kable_styling()

```

__Variable Oedema__


:::statacode
gen str1 oedema = "n"  

*replace oedema = "y" if an5==1 

*replace oedema = " " if an5==3 | an5==7 | an5==9 | an5==. 

desc oedema
:::


Just got to learn from Dr C. Oldiges that * is the R equivalent of #

```{r variable_oedema}
ch_dta %<>%
  mutate(
    oedema = "n"
  )

```

__Variable Smpling weight__

:::statacode
clonevar  sw = chweight 
:::

```{r varible_samplingweight}
ch_dta %<>%
  mutate(
    sw = chweight
  )
```


__Using the `{anthro}` package: equivalent ot running the ado file__


```{r}
pmap(list(sex = ch_dta$gender,
  age = ch_dta$age_days,
  is_age_in_month = FALSE,
  weight = ch_dta$weight,
  lenhei = ch_dta$height,
  measure = ch_dta$measure,
  oedema = ch_dta$oedema),
  anthro_zscores) -> test

reduce(test,rbind) -> test

head(test)

names(test)
```

__Notice the deviations from stata file, there is no need to use the `ageunit` variable as the `anthro_zscores()` function has an argument,`is_age_in_month`, that takes a logical for age unit. Secondly, there is no provision for an argument in the `anthro_zscores()` for the `sw` variable, hence I have not useed it.__

Now binding the `test` object to the `ch_dta` object.

```{r}
bind_cols(ch_dta, test) -> ch_dta
```

:::statacode
gen z_scorewa = _zwei 

replace z_scorewa = . if _fwei==1  

lab var z_scorewa "z-score weight-for-age WHO" 
:::


```{r zscorewa_nutrition}
ch_dta %<>%
  mutate(
    z_scorewa = structure(
      ifelse(fwei == 1, NA, zwei),
      label = "z-score weight-for-age WHO")
    )
```


:::statacode
gen underwa2 = (z_scorewa < -2.0) //Takes value 1 if the child is under 2 stdev below the median and 0 otherwise// 

replace underwa2 = . if z_scorewa==. 

lab var underwa2  "Child is undernourished (weight-for-age) 2sd - WHO"
:::

```{r underweight_nutrition}
ch_dta %<>%
  mutate(
    underwa2 = structure(
      ifelse(
        is.na(z_scorewa),
        NA,
        z_scorewa < -2.0
      ),
      label = "Child is undernourished (weight-for-age) 2sd-WHO"
    )
  )
```

:::statacode
gen underwa3 = (z_scorewa < -3.0) //Takes value 1 if the child is under 3 stdev below the median and 0 otherwise// 

replace underwa3 = . if z_scorewa==. 

lab var underwa3  "Child is undernourished (weight-for-age) 3sd - WHO" 
:::

```{r ultrapoverty_nutrition}
ch_dta %<>%
  mutate(
    underwa3 = structure(
      ifelse(
        is.na(z_scorewa),
        NA,
        z_scorewa < -3.0
      ),
      label = "Child is undernourished (weight-for-age) 3sd-WHO"
    )
  )
```

:::statacode
gen stunting = (_zlen < -2.0) 

replace stunting = . if _zlen == . | _flen==1 

lab var stunting "Child is undernourished (lenght/height-for-age) 2sd - WHO" 

gen stunting3 = (_zlen < -3.0) 

replace stunting3 = . if _zlen == . | _flen==1 

lab var stunting3 "Child is undernourished (lenght/height-for-age) 3sd - WHO"
:::

```{r stunting_nutrition}
ch_dta %<>%
  mutate(
    stunting = structure(
      ifelse(
        flen == 1| is.na(zlen),
        NA,
        zlen < -2.0
      ),
      label = "Chlid is undernourished (length/height-for-age 2sd-WHO)"
    ),
  stunting3 =structure(
      ifelse(
        flen == 1| is.na(zlen),
        NA,
        zlen < -3.0
      ),
      label = "Chlid is undernourished (length/height-for-age 3sd-WHO)"
    )
  )
```


:::statacode
gen wasting = (_zwfl < - 2.0) 

replace wasting = . if _zwfl == . | _fwfl == 1 

lab var wasting  "Child is undernourished (weight-for-lenght/height) 2sd - WHO" 

gen wasting3 = (_zwfl < - 3.0) 

replace wasting3 = . if _zwfl == . | _fwfl == 1 

lab var wasting3  "Child is undernourished (weight-for-lenght/height) 3sd - WHO" 
:::

```{r wasting_nutrition}
ch_dta %<>%
  mutate(
    wasting = structure(
      ifelse(
        (fwfl == 1| is.na(zwfl)),
        NA,
        zlen < -2.0
      ),
      label = "Child is undernourished (weight-for-lenght/height) 3sd - WHO"
    ),
  wasting3 =structure(
      ifelse(
        (fwfl == 1| is.na(zwfl)),
        NA,
        zlen < -3.0
      ),
      label = "Child is undernourished (weight-for-lenght/height) 3sd - WHO"
    )
  )

```

:::statacode
keep  ind_id hl4 cage hh1 hh2 ln chweight child_CH z_score* under* stun* wast* _*  

order ind_id hl4 cage hh1 hh2 ln chweight child_CH z_score* under* 
:::

```{r saving_ch}
ch_dta %>% 
  select(
    ind_id,hl4,cage,hh1,hh2,ln,chweight,
    child_CH, dplyr::starts_with("z_score"),
    dplyr::starts_with("under"),dplyr::starts_with("stun"),
    dplyr::starts_with("wast"),clenhei:fss
  ) %>% 
  write_csv(here("data","npl_CH.csv"))

```

Taking means (non weighted) of underwa, wasting and stunting for comparision.

```{r comparision_ado}
ch_dta %>% 
  summarise(
    mean_z_Scorewa = mean(z_scorewa, na.rm = T),
    mean_underwa2 = mean(underwa2, na.rm = T),
    mean_underwa3 = mean(underwa3, na.rm = T),
    mean_stunting = mean(stunting, na.rm = T),
    mean_stunting3 = mean(stunting3, na.rm = T),
    mean_wasting = mean(wasting, na.rm = T),
    mean_wasting3 = mean(wasting3, na.rm = T),
  ) %>% 
  knitr::kable()%>%
  kableExtra::kable_styling()%>%
  scroll_box(width = "100%", height = "400px")
  
  
  
  
```

It is confirmed that the results shown above match with the results generated by STATA do file.

## Step 1.2: WH -Women Level (all eligible females between 15-49 years in the household)

:::statacode
use "$workingfolder_in\wm.dta", clear  

rename _all, lower 
:::

```{r import_wm} 
read_sav(here("data","wm.sav")) -> wm_dta

clean_names(wm_dta) -> wm_dta
```

:::statacode
gen double ind_id = hh1*100000 + hh2*100 + ln //Please check length of variables for a correct generation of the id variable// 

format ind_id %20.0g label var ind_id "Individual ID" 
 
duplicates report ind_id 
 
gen women_WM = 1 //Identification variable for observations in WM recode// 

ta ma5 cm1,m //No subsample of ever-married women// 
:::

```{r indid_wm}
wm_dta %<>%
  mutate(
    ind_id = structure(
      hh1*100000 + hh2*100 + ln,
      label = "Individual ID")
  )

## The following three steps can be written as a funciton that returns the number of duplicate IDS or creates a column in the data that marks if the ind id is duplicate or not

table(wm_dta$ind_id) %>% 
  as.data.frame %>% 
  filter(Freq>1) -> wm_dta_duplicate_ind_id #step1

wm_dta %<>%
  mutate(
    duplicates = ind_id  %in% wm_dta_duplicate_ind_id$Var1
  ) #step2

unique(wm_dta$duplicates) #step3


wm_dta %<>%
  mutate(
    women_WM = 1
  )

wm_dta %>% 
  tabyl(ma5, cm1, show_na = T) %>%
  gt()
```

:::statacode
keep wb2 wm7 cm1 cm8 cm9a cm9b cm10 ma1 ma5 ind_id women_WM wmweight ta1-ta17 

save "$workingfolder_out\npl14_WM.dta", replace 
:::

```{r keep_columns_WM}
wm_dta %>% 
  select(wb2, wm7, cm1, cm8, cm9a, cm9b, cm10, ma1, ma5,
         ind_id, women_WM, wmweight, ta1:ta17) %>% 
  write_csv(here("data", "npl14_WM.csv"))

```

## Step 1.3: HH - HOusehold Characterstics

:::statacode
use "$workingfolder_in\hh.dta", clear //Change to the corresponding HH-file//  

rename _all, lower 
:::

```{r import_HH}
read_sav(here("data","hh.sav")) -> hh_dta

clean_names(hh_dta) -> hh_dta
```

:::statacode
gen double hh_id = hh1*1000 + hh2 //Please check length of variables for a correct generation of the id variable// 

format hh_id %20.0g 

lab var hh_id "Household ID" 
:::

```{r hhid_HH}
hh_dta %<>%
  mutate(
    hh_id = structure(
      hh1*1000 + hh2,
      label = "Household ID")
  )

```

:::statacode
save "$workingfolder_out\npl14_HH.dta", replace 
:::

```{r data_store_hh}
hh_dta %>% 
  write_csv(here("data","npl14_HH.csv"))
```

## Step 1.4: No Male Recode, but Birth recode 

:::statacode
*use "$workingfolder_in\mn.dta", clear //Change to the corresponding MN-file// 

rename _all, lower 
:::

__Note that there is no mn.dta or mn.sav available to perform operations as performed in STATA do file. Operations on mn.dta or mn.sav file will be skipped as long as the necessary file is not available__

Moving on.

:::statacode
use "$workingfolder_in\bh.dta", clear  

rename _all, lower 
:::

```{r import_bh}
read_sav(here("data","bh.sav")) -> bh_dta

clean_names(bh_dta) -> bh_dta
```

:::statacode
gen double ind_id = hh1*100000 + hh2*100 + ln //Please check length of variables for a correct generation of the id variable// 

format ind_id %20.0g 

label var ind_id "Individual ID" 
 
gen double ind_c = hh1*10000000 + hh2*10000 + ln*100 + bhln //Please check length of variables for a correct generation of the id variable// 
 
duplicates report ind_c 
 
gen women_BH = 1 //Identification variable for observations in WM recode// 
:::


```{r ids_bh}
bh_dta %<>%
  mutate(
    ind_id = structure(
      hh1*100000 + hh2*100 +ln,
      label = "Individual ID"),
    ind_c = hh1*10000000 + hh2*10000 + ln*100 + bhln
  )

# 3 step check for duplicate ind_C

table(bh_dta$ind_c) %>% 
  as.data.frame %>% 
  filter(Freq>1) -> bh_dta_duplicate_ind_c #step1

bh_dta %<>%
  mutate(
    duplicates = ind_c  %in% bh_dta_duplicate_ind_c$Var1
  ) #step2

unique(bh_dta$duplicates) #step3

bh_dta %<>%
  mutate(
    women_BH = 1
  )
```

:::statacode
bys ind_id: egen tbirths_=max(bhln)   

ta bh5 bh9u,m  //only not alive offspring has age at death 

keep wmweight hh1 hh2 ln tbirths_ bhln bh5 bh9* ind_id women_BH 
:::

```{r tbirths_bh}
bh_dta %<>%
  group_by(ind_id) %>% 
  mutate(
    tbirths_ = max(bhln, na.rm = T)
  ) %>% 
  ungroup()

bh_dta %>% 
  tabyl(bh5, bh9u, show_na = T) %>% 
  gt()

bh_dta %>% 
  select(wmweight, hh1, hh2, ln, tbirths_, bhln, 
         bh5, dplyr::starts_with("bh9"), ind_id, women_BH) -> subset_bh_dta
```


:::statacode
bys bh9f : ta bh9c bh5 ,m  //all but 1 of 15 imputations are under 5 years old, most of them lack of unit This dofile relies on the imputation. 

bys bh9f : ta bh9c bh9u if bh9f>=7 & bh9f<=8 ,m  //all but 1 of 15 imputations are under 5 years old, most of them lack of unit This dofile relies on the imputation. 
:::


```{r tables_bys_bh9f}
subset_bh_dta %>% 
  tabyl(bh9c,bh5,bh9f, show_na = T) 

subset_bh_dta %>% 
  filter(bh9f >=7,bh9f<=8) %>% 
  tabyl(bh9c,bh9u,bh9f, show_na = T) 

```

:::statacode
gen dufive_ = cond(bh9c<60,1,0) 

replace dufive_ = . if bh9c == . 

ta bh9f dufive, m   //2072 deaths of under five of which 14 has imputed age, 10 of them we have no further info. 

ren bh5 bh5_  

ren bh9* bh9*_ 
:::


```{r dufive_bh}
subset_bh_dta %<>%
  mutate(
   dufive_ = ifelse(bh9c < 60,1,0),
   dufive_ = ifelse(is.na(bh9c),NA,dufive_)
  )

subset_bh_dta %>% 
  tabyl(bh9f,dufive_, show.na =T) %>%
  knitr::kable()%>%
  kableExtra::kable_styling()%>%
  scroll_box(width = "100%", height = "100%")

subset_bh_dta %<>%
  rename(bh5_ = bh5) %>% 
  rename_at(.vars = vars(dplyr::starts_with("bh9")), 
            .funs = ~str_c(.,"_"))

names(subset_bh_dta)  
```

:::statacode
reshape wide bh5 bh9* dufive_, i(ind_id) j(bhln)

egen tdufive = rowtotal(dufive_*)

ta tdufive, m //1110+(289*2)+(3*74)+(4*20)+(5*7)+47 = 2072 deaths under five which coincide with the original dataset
:::



```{r reshape_bh}
subset_bh_dta %<>%
  pivot_wider(names_from = bhln,values_from = c(bh5_,dplyr::starts_with("bh9"),dufive_ ),names_sep = "")

subset_bh_dta %<>%
  mutate(
    tdufive = rowSums(.[,c(68:79)],na.rm = T)
  )

subset_bh_dta %>% 
  tabyl(tdufive, show_na = T) %>% 
  gt()
```

:::statacode
save "$workingfolder_out\npl14_BH.dta", replace
:::

```{r saving_subsetbh} 
subset_bh_dta %>% 
  write_csv(here("data","npl14_BH.csv"))
```

## Step 1.5 HL - Household Member Level

:::statacode
use "$workingfolder_in\hl.dta", clear

rename _all, lower 
:::

```{r improt_hl}
read_sav(here("data","hl.sav")) -> hl_dta

clean_names(hl_dta) -> hl_dta
```

:::statacode
gen country = "Nepal"

gen year_published = "2014"

gen year = 2014

gen survey = "MICS"

gen double hh_id = hh1*1000 + hh2 //Please check length of variables for a correct generation of
the id variable//

label var hh_id "Household ID"

gen double ind_id = hh1*100000 + hh2*100 + hl1 //Please check length of variables for a correct
generation of the id variable//

label var ind_id "Individual ID"
:::


```{r ids_hl}
hl_dta %<>%
  mutate(
    country = "Nepal",
    year_published = "2014",
    year = 2014,
    survey = "MICS",
    hh_id = structure(
      hh1*1000 + hh2,
      label = "Household ID"
    ),
    ind_id = structure(
      hh1*100000 + hh2*100 + hl1,
      label = "Individual ID"
    )
  )
```


## Data Merging (HL, WM, CH) & Control Variables

### Step 1.6a: Data Merging - WM recode

:::statacode
merge 1:1 ind_id using "$workingfolder_out\npl14_WM.dta" 
:::


```{r join1}

hl_dta %>% 
  left_join(wm_dta %>% 
  select(wb2, wm7, cm1, cm8, cm9a, cm9b, cm10, ma1, ma5,
         ind_id, women_WM, wmweight, ta1:ta17),
  by = c("ind_id" = "ind_id")
) -> merged_data
```


:::statacode
gen temp = (hl7>0)

tab women_WM temp, miss col

tab wm7 if temp==1 & women_WM==. //Total of eligible women not interviewed//

ta hl6 hl4 if _m==1,m //only men and non-eligible women are not merged.

drop temp _merge 
:::


```{r join1_tables}
merged_data %<>%
  mutate(
    temp = hl7 >0
  )

merged_data %>% 
  tabyl(women_WM, temp, show_na = T) %>% 
  gt()

merged_data %>% 
  filter(temp ==1,is.na(women_WM)) %>% 
  tabyl(wm7, show_na = T) 

# there is no variable `_m`

merged_data %<>%
  select(-temp)
```

:::statacode
merge m:1 hh_id using "$workingfolder_out\npl14_HH.dta"

ta hh9 if _m==2,m

drop if _merge==2

drop _merge
:::

```{r join2}

merged_data %<>%
  left_join(hh_dta, by = c("hh_id" = "hh_id"))

# there os no _m variable

# there is no _merge variable
```


:::statacode
merge 1:1 ind_id using "$workingfolder_out\npl14_CH.dta"

count if ln==0 //The children without household line are unique to the CH Recode// 

ta hl6 if _m==1,m //only 5 years old and older are not merged.

replace hh_id = hh1*1000 + hh2 if ln==0 //Creates hd_id for children without household line, but
this is not a problem //

drop _merge 
:::

```{r join3}
merged_data %<>%
  left_join(ch_dta %>% 
  select(
    ind_id,hl4,cage,hh1,hh2,ln,chweight,
    child_CH, dplyr::starts_with("z_score"),
    dplyr::starts_with("under"),dplyr::starts_with("stun"),
    dplyr::starts_with("wast"),clenhei:fss
  ),
  by = c("ind_id" = "ind_id")
  )

# there is no variable _m

merged_data %<>%
  mutate(
    hh_id = ifelse(ln==0, hh1*1000+hh2,hh_id)
  )

# there is no variable _merge
```

:::statacode

merge 1:1 ind_id using "$workingfolder_out\npl14_BH.dta"

ta cm1 if _m==1,m //only those who have not given birth are not merged.

drop _merge
:::

```{r join4}
merged_data %<>%
  left_join(subset_bh_dta, by = c("ind_id" = "ind_id"))

#there are no variables by the name _m amd _merge
```


## Step 1.6: Create control variables if household has eligible members for WM and CH Levels

:::statacode
gen fem_eligible = (hl7>0)

bys hh_id: egen hh_n_fem_eligible = sum(fem_eligible) //Number of eligible women for interview in
the hh//

gen no_fem_eligible = (hh_n_fem_eligible==0) //Takes value 1 if the household had no eligible females for an interview//

label var no_fem_eligible "Household has no eligible women" 
:::

```{r control1} 
merged_data %<>%
  mutate(
    fem_eligible = hl7>0
  ) %>% 
  group_by(hh_id) %>% 
  mutate(
    hh_n_fem_eligible = sum(fem_eligible,na.rm = T)
  ) %>% 
  ungroup() %>% 
  mutate(
    no_fem_eligible = structure(
      hh_n_fem_eligible == 0,
      label = "HOusehold has no eligible female"
    )
  )
```


:::statacode
gen child_eligible = (hl7b>0 | child_CH==1) //line number for mother/caretake for children under five//

bys hh_id: egen hh_n_children_eligible = sum(child_eligible) //Number of eligible children for anthropometrics//

gen no_child_eligible = (hh_n_children_eligible==0) //Takes value 1 if there were no eligible children for anthropometrics//

lab var no_child_eligible "Household has no children eligible" 
:::

```{r control2}
merged_data %<>%
  mutate(
    child_eligible = (hl7b>0 | child_CH == 1)
  ) %>% 
  group_by(hh_id) %>% 
  mutate(
    hh_n_children_eligible = sum(child_eligible, na.rm = T)
  ) %>% 
  ungroup() %>% 
  mutate(
    no_child_eligible = structure(
      hh_n_children_eligible ==0,
      label = "Household has no children eligible")
  )
```


:::statacode
gen no_child_fem_eligible = (no_child_eligible==1 & no_fem_eligible==1)

lab var no_child_fem_eligible "Household has no children or women eligible"
:::

```{r control3}
merged_data %<>%
  mutate(
    no_child_fem_eligible = structure(
      (no_child_eligible == 1 & no_fem_eligible ==1),
      label = "Household has not children or women eligible"
    )
  )
```

:::statacode
gen no_eligibles = (no_fem_eligible==1) //Takes value 1 if the household had no eligible members for an interview//

lab var no_eligibles "Household has no eligible women" 
:::


```{r control4}
merged_data %<>%
  mutate(
    no_eligible = structure(
      (no_fem_eligible == 1),
      label = "HOusehold has no eligible women")
  )
```


:::statcode
bys hh_id: gen id = _n

count if id==1

count

count if no_eligible==1

count if no_eligible==1 & id==1

count if no_fem_eligible==1

count if no_fem_eligible==1 & id==1

count if no_child_eligible==1 

count if no_child_eligible==1 & id==1

count if no_child_fem_eligible==1

count if no_child_fem_eligible==1 & id==1 
:::

```{r control5}
merged_data %<>%
  group_by(hh_id) %>% 
  mutate(
    id = n()
  ) %>% 
  ungroup()

nrow(merged_data %>% filter(id == 1))

nrow(merged_data %>% filter(no_eligible == 1))

nrow(merged_data %>% filter(no_eligible == 1 & id == 1))

nrow(merged_data %>% filter(no_fem_eligible == 1 ))

nrow(merged_data %>% filter(no_fem_eligible == 1 & id == 1))

nrow(merged_data %>% filter(no_child_eligible == 1 ))

nrow(merged_data %>% filter(no_child_eligible == 1 & id == 1))

nrow(merged_data %>% filter(no_child_fem_eligible == 1))

nrow(merged_data %>% filter(no_child_fem_eligible == 1 & id == 1))
```


# Step 2: Data Preparation 

## Standardization of 10 indicators and identification of deprived individuals


:::statacode
clonevar urban = hh6 //Type of place of residency: urban/rural//

replace urban = 0 if urban == 2 //Redefine the coding and labels to 1/0//

label define lab_urban 1 "urban" 0 "rural"

label values urban lab_urban 

clonevar relationship = hl3 //Relationship to the head of household/
:::


```{r urban_step2}
merged_data %<>%
  mutate(
    urban = structure(
      ifelse(hh6.x==2,0,hh6.x),
      labels = c("urban" = 1, "rural" = 0) 
    ),
    relationship = hl3
  )
```

:::statacode
clonevar sex = hl4 //Sex household member//

replace sex = 0 if sex==2 //Redefine the coding and labels to 1/0//

replace sex = . if sex==9 //No missing values

label define sex 1"male" 0 "female" 

label val sex sex

clonevar age = hl6 //Age household member//

replace age = . if age==98 | age==99 // no missing values 

:::

```{r sex_step2}
merged_data %<>%
  mutate(
    sex = structure(
      ifelse(hl4.x==9,NA,
             ifelse(hl4.x == 2, 0,hl4.x)),
      labels = c("male" = 1, "female" = 0)
    ),
    age = ifelse((hl6 == 98|hl6==99),NA, hl6)
  )
```

:::statacode
by hh_id: gen temp = _n

by hh_id: egen hhs = max(temp)

label var hhs "Household size"

drop temp

decode hh7, gen(temp)

encode temp, gen(region)
:::

```{r householdsize_step2}
merged_data %<>%
  group_by(hh_id) %>% 
  mutate(
    temp = n(),
    hhs = structure(
      max(temp, na.rm = T),
      label = "Household size"
    )
  ) %>% 
  ungroup() %>% 
  select(-temp) %>% 
  mutate(
    region = hh7.x
  )
```

## Step 2.3: Nutrition

:::statacode
gen hh_no_low_bmi = .

gen f_low_bmi = .

gen m_low_bmi = . 
:::

```{r nutri1}
merged_data %<>%
  mutate(
    hh_no_low_bmi = NA,
    f_low_bmi = NA,
    m_low_bmi = NA
  )
```


:::statacode
bys hh_id: egen temp = max(underwa2)

gen hh_no_underwa2 = (temp==0) //Takes value 1 if no child in the hh is underweighted, 0 if at least one is//

replace hh_no_underwa2 = . if temp==.

drop temp

lab var hh_no_underwa2 "Household has no child under weight-for-age – 2 stdev" 

replace hh_no_underwa2 = 1 if no_child_eligible==1
:::


```{r nutri2}
merged_data %<>%
  group_by(hh_id) %>% 
  mutate(
    temp = max(underwa2)
  ) %>% 
  ungroup() %>% 
  mutate(
    hh_no_underwa2 = structure(
      ifelse(no_child_eligible==1,1,ifelse(is.na(temp),NA,(temp==0))),
      label = "Household has no child under weight-for-age – 2 stdev")
  ) %>% 
  select(-temp)
```


:::statacode
bys hh_id: egen temp = max(underwa3)

gen hh_no_underwa3 = (temp==0) //Takes value 1 if no child in the hh is underweighted, 0 if at least one is//

replace hh_no_underwa3 = . if temp==.

replace hh_no_underwa3 = 1 if no_child_eligible==1

lab var hh_no_underwa3 "Household has no child under weight-for-age - 3 stdev"

drop temp 
:::


```{r nutri3}
merged_data %<>%
  group_by(hh_id) %>%
  mutate(
    temp = max(underwa3)
  ) %>% 
  ungroup() %>% 
  mutate(
    hh_no_underwa3 = structure(
      ifelse(no_child_fem_eligible == 1, 1,
             ifelse(is.na(temp),NA,temp ==0)),
      label = "Household has no child under weight-for-age - 3 stdev"
    )
  ) %>% 
  select(-temp)
  
```


:::statacode
gen hh_nutrition = hh_no_underwa2 

label var hh_nutrition "Household has no child undernourished (weight-for-age)"

replace hh_nutrition = 1 if no_child_eligible==1

gen hh_nutrition_3_17 = hh_no_underwa3

replace hh_nutrition_3_17 = 1 if no_child_eligible==1

lab var hh_nutrition_3_17 "Household has no child undernourished (weight-for-age)" 
:::

```{r nutri4}
merged_data %<>%
  mutate(
    hh_nutrition = structure(
      ifelse(no_child_eligible == 1,1,hh_no_underwa2),
      label = "Household has no child undernourished (weight-for-age)"
    ),
    hh_nutrition_3_17 = structure(
      ifelse(no_child_eligible == 1,1,hh_no_underwa3),
      label = "Household has no child undernourished (weight-for-age)"
    )
  )
```



## Nutri checkk 

```{r fingerscrossed} 
merged_data %>% 
  summarise(
    average_unweighted_hh_nutrition = mean(hh_nutrition,na.rm = T),
    average_unweighted_hh_nutrition_3_17 =
      mean(hh_nutrition_3_17,na.rm = T),
  )
```








