---
title: "Well Being Index"
output: 
  html_document: 
    css: STATAcode.css
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Nepal Well Being Index 

MICS 2014 data is used to create this Index. Through out this document a convention is maintained where the STATA code will be provided as reference to the equivalent  R code.

The STATA code provided as referecne will show up as follows[^1]:

:::statacode
Reference STATA code will appear in such boxes.
:::

[^1]: Icons made by <a href="https://www.flaticon.com/authors/xnimrodx" title="xnimrodx">xnimrodx</a> from <a href="https://www.flaticon.com/" title="Flaticon"> www.flaticon.com</a>

## Libraries

```{r libraries}
library(here)
library(tidyverse)
library(janitor)
library(magrittr)
library(knitr)
library(kableExtra)
library(gt)
```

## Step1: Data Preparation

Comment from STATA code:

_Selecting main variables from WM and CH recode and merging with HL recode._  

### Step1.1: CH - Children's Level (Children Under 5)


```{r}

```

