---
title: "Well Being Index"
author: "Ayush Patel"
date: "`r Sys.Date()`"
output: 
  html_document: 
    css: STATAcode.css
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{css ,echo = FALSE}
h1, h2, h3 {
  text-align: center;
  color: #303960;
}
```

__Nepal Well Being Index __

MICS 2014 data is used to create this Index. Through out this document a convention is maintained where the STATA code will be provided as reference to the equivalent  R code.

The STATA code provided as referecne will show up as follows[^1]:

:::statacode
Reference STATA code will appear in such boxes.
:::

[^1]: Icons made by <a href="https://www.flaticon.com/authors/xnimrodx" title="xnimrodx">xnimrodx</a> from <a href="https://www.flaticon.com/" title="Flaticon"> www.flaticon.com</a>

# Libraries

```{r libraries}
library(here)
library(tidyverse)
library(haven)
library(janitor)
library(magrittr)
library(knitr)
library(kableExtra)
library(gt)
library(anthro)
```

# Step1: Data Preparation

Comment from STATA code:

_Selecting main variables from WM and CH recode and merging with HL recode._  

## Step1.1: CH - Children's Level (Children Under 5)


:::statacode
use "$workingfolder_in\ch.dta", clear //Change to the corresponding CH-file// 
:::

Note that the STATA code imports the .dta file, we have the same data in .sav format. We will be using these files.

```{r dataimport_ch}
ch_dta <- read_sav(here("data","ch.sav"))

```

### Step1.1a: Key variable for merging


:::statacode
rename _all, lower 
:::

```{r}
ch_dta <- clean_names(ch_dta)
```

:::statacode
gen double ind_id = hh1*100000 + hh2*100 + ln 

//Please check length of variables for a correct generation of the id variable// 

format ind_id %20.0g 

label var ind_id "Individual ID" 
:::

```{r Indid_ch}
ch_dta %<>%
  mutate(
    ind_id = structure(
      hh1*100000 + hh2*100 + ln,
      label = "Individual ID"
    )
  )
```


:::statacode
duplicates report ind_id 

duplicates tag ind_id, gen(duplicates) 

tab ln if duplicates!=0 //A number of children are not listed in the household// 
:::

```{r ch_duplicate_ind_id}
(nrow(ch_dta) == length(unique(ch_dta$ind_id)) 
 & sum(is.na(ch_dta$ind_id)) == 0) ## Returns on True if ind_id has no duplicates

# creating a table of ind_ids that are duplicatess
table(ch_dta$ind_id) %>% 
  as.data.frame %>% 
  filter(Freq>1) -> ch_dta_duplicate_ind_id

ch_dta %<>%
  mutate(
    duplicates = ind_id  %in% ch_dta_duplicate_ind_id$Var1
  ) 

ch_dta %>%
  filter(duplicates == 1) %>% 
  tabyl(ln, show_na = T)
```

:::statacode
bys ind_id: gen line = (_n) 

replace ind_id =  hh1*100000 + hh2*190 + line if duplicate!=0 //We assume consecutive hh line starting at 90// 
 
duplicates report ind_id //We should not have any duplicate at this stage// 
 
gen child_CH = 1 //Identification variable for observations in CH recode// 
:::

```{r removing_duplicates_if_any}
ch_dta %<>%
  group_by(ind_id) %>% 
  mutate(line = n()) %>% 
  ungroup()
  
ch_dta %<>% 
  mutate(
    ind_id = structure(
      ifelse(duplicates != 0,
             hh1*100000 + hh2*190 + line, ind_id),
      label = "Individual ID"
    ),
    child_CH = 1
  )

(nrow(ch_dta) == length(unique(ch_dta$ind_id)) 
 & sum(is.na(ch_dta$ind_id)) == 0) ## Returns on True if ind_id has no duplicates
```

### Step 1.1b: Children Nutrition


__Variable Sex__

:::statacode
tab hl4, miss //Check the variable for "sex" has "1" for male, "2" for female and all missing values are "."// 

gen gender = hl4 

desc gender 

tab gender 

label define gender 1"male" 2"female", replace 

label values gender gender 
:::


```{r variable_sex_nutrition}
str(ch_dta$hl4)

ch_dta %<>%
  mutate(
    gender = structure(
      hl4,
      labels = c("male"  = 1, "female" = 2) 
    )
  )

str(ch_dta$gender)
```

__Variable Age__

:::statacode
ta cage,m //Check all missing values are "."// 

ta caged,m //Check all missing values are "."// 

codebook cage caged //Check unit of measure – in this case age is measured in months// 

clonevar age_months = cage  

clonevar age_days = caged 

replace age_months = . if cage==99 //No missing data here// 

gen str6 ageunit = "days" //We define the unit of measure, in this case age is measured in months, otherwise please change to ageunit = "days"// 
lab var ageunit "Days" 
:::


```{r variable_age_nutrition}
sum(is.na(ch_dta$cage))

sum(is.na(ch_dta$caged))

ch_dta %<>%
  mutate(
    age_months = ifelse(cage==99, NA, cage),
    age_days = caged,
    ageunit = structure("days", label = "Days")
  )
```

__Variable body weight[^2]__

[^2]: It must be in kilograms

:::statacode
ta an3, miss //Check all missing values are "."//  

codebook an3 //Check unit of measure – in this case weight is measured in kilograms// 

clonevar weight = an3  

desc weight  

replace weight = .  if an3>=99 //All missing values or out of range are replaced as "."// 

tab an2 an3 if an3>=99 | an3==., miss //an2: result of the measurement// summ weight 
:::

```{r variable_bodyweight_nutrition}
sum(is.na(ch_dta$an3))

str(ch_dta$an3)

ch_dta %<>%
  mutate(
    weight = ifelse(an3 >=99, NA, an3)
  )

ch_dta %>% 
  filter(an3 >=99 | is.na(an3)) %>% 
  tabyl(an2, an3,show_na = T) %>%
  knitr::kable()%>%
  kableExtra::kable_styling()
  
  
  
  
  
```


__Variable height[^3]__

[^3]: It mus be in centimeters

:::statacode
ta an4, miss //Check all missing values are "."//  

codebook an4 //Check unit of measure – in this case age is measured in centimetres// 

clonevar height = an4 

desc height  

replace height = . if an4>=999 //All missing values or out of range are replaced as "."// 

summ height ## Not sure what this command means

codebook an4a gen measure = "l" if an4a==1 //Child measured lying down// 
replace measure = "h" if an4a==2 //Child measured standing up// 

replace measure = " " if an4a==. // No information  

replace measure = " " if an4a==9 //Replace with " " if unknown or missing//

:::


```{r varible_height_nutrition}
sum(is.na(ch_dta$an4))

str(ch_dta$an4)

ch_dta %<>%
  mutate(
    height = ifelse(an4 >= 999, NA, an4),
    measure = case_when(
      is.na(an4a) ~ "",
      an4a == 9 ~ "",
      an4a == 1 ~ "l",
      an4a == 2 ~ "h"
    )
  )
```


:::statacode
tab an2 an4 if an4>=999 | an4==., miss  

tab measure,m 

:::

```{r tabs_height_variables}

ch_dta %>% 
  filter(an4 >= 999 | is.na(an4)) %>% 
  tabyl(an2, an4, show_na = T)%>%
  knitr::kable()%>%
  kableExtra::kable_styling()
  
ch_dta %>% 
  tabyl(measure, show_na = T) %>%
  knitr::kable()%>%
  kableExtra::kable_styling()

```

__Variable Oedema__

:::statcode
gen str1 oedema = "n"  

*replace oedema = "y" if an5==1 

*replace oedema = " " if an5==3 | an5==7 | an5==9 | an5==. 

desc oedema
:::


Just got to learn from Dr C. Oldiges that * is the R equivalent of #

```{r variable_oedema}
ch_dta %<>%
  mutate(
    oedema = "n"
  )

```

__Variable Smpling weight__

:::statcode
clonevar  sw = chweight 
:::

```{r varible_samplingweight}
ch_dta %<>%
  mutate(
    sw = chweight
  )
```

